\cvsection{Extracurricular Activity}

\begin{cventries}
\cventry
    {VP External}
    {Vice President of External Affairs at McGill Student's Flying Club (MSFC)}
    {Quebec, Canada}
    {Aug. 2017 - Ongoing}
    {
      \begin{cvitems}
        \item {Was elected to be part of the MSFC executive team.}
        \item {Participated in various activities with the MSFC; went on several day trips: skydiving, pilot for a day.}
      \end{cvitems}
    }    \newline

\cventry
    {McGill Robotics}
    {Mars Rover Arm Software Developer}
    {Quebec, Canada}
    {May 2018 - Ongoing}
    {
      \begin{cvitems}
        \item {Developped simlation plugin in C++ in Gazebo for the Mars Rover Arm Systems in ROS (Robot Operating System).}
        \item {Developped a six-axis inverse kinematics control in Movelt for the rover arm.}
        \item {Worked with a team of over 60 students on GitHub.}
      \end{cvitems}
    }    \newline
    \cventry
    {Fund Team Member}
    {Engineering Investing Group **remove?}
    {Quebec, Canada}
    {Jan. 2018 - Ongoing}
    {
      \begin{cvitems}
        \item {Perform fundamental and technical analysis on financial asset classes.}
        \item {Receive mentorship from industry professionals and academics.}
        \item {Compete in Canadian equity and derivative markets in national and international trading simulations.}
        \item {Assist info sessions and workshops on trading strategies and product structuring.}
      \end{cvitems}
    }	 \newline
\cventry
    {Aerodynamics team member}
    {McGill Formula Electric}
    {Quebec, Canada}
    {Aug. 2017 - Ongoing}
    {
      \begin{cvitems}
        \item {Learned how to use various CAD software to design objects and manufacture them.}
        \item {Learned how to do 3D printing and welding to to design and assemble a car from the ground up.}
        \item {Refined my communication abilities when coordinating tasks in a large team.}
      \end{cvitems}
    }	 \newline
  \cventry
    {Leading Air Cadet at the 803 North Shore Sabre Squadron}
    {Royal Air Cadet}
    {Quebec, Canada}
    {Aug. 2014 - Feb. 2015}
    {
      \begin{cvitems}
        \item {Went to ground school to learn about planes and how to fly them.}
        \item {Learned about leadership and chain of command.}
        \item {Developed public speaking skills.}
        \item {Refined my organizational skills.}
      \end{cvitems}
    }	 \newline
    

\end{cventries}
