\cvsection{Volunteering}

\begin{cventries}
\cventry
    {Emergency Room and General Surgeon Shadowing}
    {Doctor Shadowing}
    {Quebec, Canada}
    {Dec 2018 - Jan 2019}
    {
      \begin{cvitems}
        \item {Assisted the supervising physician in various tasks and took notes.}
        \item {Allowed to spectate live ongoing surgeries and how trauma is to be treated in the ER.}
        \item {Experienced the daily lives of doctors}
      \end{cvitems}
    }    \newline

\cventry
    {Complete various tasks for a smooth blood donation}
    {Héma-Québec}
    {Quebec, Canada}
    {Jan 2018 - Feb 2018}
    {
      \begin{cvitems}
        \item {Welcome donors and offer information.}
        \item {Communicate with blood donors so that they remain calm and distribute food.}
      \end{cvitems}
    }    \newline

  \cventry
    {A supervisor in the Biology Learning center at John Abbott College}
    {Biology Learning Center}
    {Quebec, Canada}
    {Jan. 2017 - May 2017}
    {
      \begin{cvitems}
        \item {Supervised activities at the learning center and took the names of all students that borrowed material.}
        \item {Ensured that no students left with any material belonging to the biology department.}
        \item {managed computers to achieve smooth operation for students.}
        \item {Closed the department at the end of the day.}
      \end{cvitems}
    }    \newline
    \cventry
    {A volunteer fundraiser to raise money for the Iraqi Community Center}
    {Iraqi community Center}
    {Quebec, Canada}
    {Dec. 2016 - Feb. 2017}
    {
      \begin{cvitems}
        \item {Helped in securing funds for people in need by participating in various events to promote awareness.}
        \item {Visited selected donees to deliver funds.}
      \end{cvitems}
    } \newline
    \cventry
    {Community server at the Muslim Youth of Montreal}
    {Muslim Youth of Montreal}
    {Quebec, Canada}
    {June 2016 - Nov. 2016}
    {
      \begin{cvitems}
        \item {Managed and prepared multiple events taking place at the community centre and cleaned up after the event took place.}
        \item {Coordinated food distribution for many youth.}
        \item {Organized information sessions to raise awareness.}
      \end{cvitems}
    } \newline
     \cventry
    {Research Assistant
and Contributor}
    {McGill Mac Campus}
    {Quebec, Canada}
    {Aug. 2016 - May 2017}
    {
      \begin{cvitems}
        \item {Performed various experiments in a biological laboratory and collected various data to study the clinal variation and phenology in two congeners of Phragmites australis}
        \item {Learned various techniques such as how to work in a sterile environment laboratory, how to dissect following protocol, key features to observe on a microscope, etc. }
        \item{\url{https://www.phragmites.crad.ulaval.ca/files/phragmites/Final_Thesis_Lovat.pdf}}
      \end{cvitems}
    }\newline
    \end{cventries}
